\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-18 paper.tex
Contribution Rachid - Key decisional issues

How can we restate the main challenges, in particular in term of decision
making, that human-robot interaction brings to artificial intelligence?

\fxfatal{TDB}

>>>>

Human-robot interaction and more particularly one of it major subfields
which is human-robot collaboration provides a rich and renewed context
and challenge for the decisional abilities of a robot.
Indeed, the context where a robot has to achieve a task together with
humans gives rise to the following questions, each of them being a
challenge of is own for the robot decisional capabilities  what, who,
when; where and how ?

\emph{What to do next,} at different levels of abstractions and taking into
account several not only the current state but also the a long term
goal, is the basic or standard question for an intelligent robot. Its
is enriched here by complementary considerations dealing with the
physical and mental state of its human partner, the set of possible
actions are enriched by communication robot acts.

\emph{Who should act now} is of key importance and need also to be
decided upon by the robot. Indeed, it is sometimes better - one could
say ``more intelligent'' - for the robot to wait and leave ist human
partner act. Turn-taking opens various decisional challenges.

\emph{When to perform a given action} is enriched here by the
human-context since it has take into account the human, his needs, his
rhythms and his mental state. While performing its share of the task
the robot will have to produce signals towards the human and to
respond to signals produced by him at the proper pace.

\emph{Where to perform an action} plays an important role in presence of
humans since here again, the choice is not trivial and might need
elaborated decision. Robot here has to take into account effort
sharing, visibility of its action by the human, disturbance or
discomfort  induced by its action.

\emph{How to perform an action} plays a key role when it comes to a
robot which has to interact with humans. Very often, there are
numerous ways to perform an action or to achieve a goal. Deciding which
one to perform is a non trivial decision problem. One way to take into
account this aspect is to develop cost-based planners which tend to
search for plans that satisfy an acceptable "cost" in terms, for
instance, of ``acceptability'' or ``legibility''.

It is also clear that these different questions are not independent
and should often be considered in one decision step. The human-aware task and
motion planners, which we have built, are instances of systems which
have been specially designed to deal with this intricacy.

In one word, the quality of the decision will be measured here in
terms of ``pertinence'' of robot behaviour. This notion covefrs
several aspects as dicussed above, including efficiency.
